CASTRO: A New Compressible Astrophysical Solver. IV. Performance Portability

### 2018-11-04 gpus/paper.tex
more outline
software

@@

>>>>

\subsection{Summary of changes required}

The main hydrodynamics solver in \castro\ is an unsplit corner
transport upwind \citep{ppmunsplit} piecewise parabolic method
\citep{ppm} scheme.  This uses full corner coupling, requiring a 
number of transverse Riemann problem solutions.

\section{Reaction networks}

@@

Our current focus is on offloading the hydrodynamics and reactions to
GPUs, so we will achieve the best GPU performance for problems without
self-gravity.

\software{MPICH, GCC, Castro, python, matplotlib}
